REVISITING SEMI-CONTINUOUS HIDDEN MARKOV MODELS

### 2011-09-28 misc/papers/icassp12_tied/icassp12.tex
Minor futher changes to paper.
git-svn-id: https://svn.code.sf.net/p/kaldi/code/sandbox/discrim@532 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

\begin{abstract}
In the past decade, semi-continuous hidden Markov models (SC-HMMs) have not 
attracted much attention in the speech recognition community. Growing amounts 
of training data and increasing sophistication of model estimation led to the 
impression that continuous HMMs are the best choice of acoustic model.
%
However, recent work on recognition of under-resourced languages faces the same
old problem of estimating a large number of parameters from limited amounts 
of transcribed speech.
This has led to a renewed interest in methods of reducing the number of parameters 
while maintaining or extending the modeling capabilities of continuous models.
%
In this work, we compare classic and multiple-codebook semi-continuous models 
that use full covariance matrices with continuous HMMs and subspace Gaussian mixture models.
%
Experiments using on the RM and WSJ corpora show that a semi-continuous system
can still yield competitive results while using fewer Gaussian components.
Our best semi-continous systems included full-covariance codebook Gaussians,
multiple codebooks, and smoothing of the weight parameters.
\end{abstract}

>>>>

\begin{abstract}
In the past decade, semi-continuous hidden Markov models (SC-HMMs) have not 
attracted much attention in the speech recognition community. Growing amounts 
of training data and increasing sophistication of model estimation led to the 
impression that continuous HMMs are the best choice of acoustic model.
%
However, recent work on recognition of under-resourced languages faces the same
old problem of estimating a large number of parameters from limited amounts 
of transcribed speech.
This has led to a renewed interest in methods of reducing the number of parameters 
while maintaining or extending the modeling capabilities of continuous models.
%
In this work, we compare classic and multiple-codebook semi-continuous models
using diagonal and full covariance matrices with continuous HMMs and subspace Gaussian 
mixture models.  
Experiments using on the RM and WSJ corpora show that while a classical semi-continous
system does not perform as well as a continuous one, multiple-codebook semi-continuous
systems can perform better, particular when using full-covariance Gaussians.
\end{abstract}
